---
title: "Community detection to find similrar components connecting each other"
author: "niki"
date: "18 December 2017"
output: html_document
---

## R Markdown
Find the community structure / group node neighbours together.


#[0]----------------SET STEERING PARAMETERS-----------------------------------------------#placeholders
```{r}

r_fpath = "H:/theis_work/SWC_chair_ml_related/Archi_data/03airport_version3//"
r_f1name = "elements"
r_f2name = "relations"


```


#[1]--------------IMPORT DATASET IN MEMORY FROM DIRECTORY-------------------------------
```{r}
#Upload csv into memory
#Inputparameters:
# - i.fpath: Directory where csv file available
# - i.fname: File name to read/import


read_data <- function(i.fpath, i.fname) { 
  library(readr)
  
  #Bring csv file path and file name together
  fpath <- paste(i.fpath, i.fname, ".csv", sep = "")
  
  #Read csv from path and the given file name
  #Supress warnings because of data from IBM
  df_csv <- suppressWarnings(read_csv(fpath, col_names = TRUE))
  
  return (df_csv)
}
#Store csv in dataframe
elements <- suppressWarnings(read_data(r_fpath, r_f1name))
relations <- suppressWarnings(read_data(r_fpath, r_f2name))

#Retrives the dimension of an object (rows and columns)
dim(elements)
dim(relations)
```

#[2]--------------COMBINE THE DATA FROM MATCHING ELEMENTS AND RELATION DATAFRAME-------------------------------
```{r}
combined_data<- function(df){
  
  new_ele<-elements[match(relations$Source, elements$ID), 3, drop=F]
  new_rel<-elements[match(relations$Target, elements$ID), 3, drop=F]
  
  df<-cbind(new_ele,new_rel)   #new dataframe
  
  #change column names
  colnames(df)[1] <- "new_source"
  colnames(df)[2] <- "new_target"
  
  #combine with the relation2 table
  data<-cbind(relations, df)
  
  
  data$Source<- NULL
  data$Target<- NULL
  
  return(data)
}
data<- combined_data()
dim(data)
```

#[2]--------------GENERATE GRAPH DATA FROM DATAFRAME-------------------------------

```{r}
#generate Igraph object from dataframe
library(igraph)
g1 <- graph_from_data_frame(data[, 5:6], directed = TRUE)
g1
```


#[3]--------------FIND COMMUNITIES USING IGRAPH COMMUNITY ALGORITHMS-------------------------------


```{r}
#parameters
#clus_btw: edge-betweenness community
#clus_sgc: spinglass community
#clus_wtc: walktrap community
#clus_inf: infomap community
#clus_evc: leading eigenvector community
#clus_lpc: label propagation community


#1) Edge betweenness cluster
clus_btw<- cluster_edge_betweenness(g1, directed = TRUE)
communities(clus_btw)
modularity(clus_btw)


#2) Spinglass cluster
#seed value is imp
set.seed(200)
clus_sgc<- cluster_spinglass(g1)
communities(clus_sgc)
modularity(clus_sgc)
#convert communities to data frame
#com <- cbind(V(g1)$name,clus_sgc$membership)

#3) Walktrap
clus_wtc<- cluster_walktrap(g1)
communities(clus_wtc)
modularity(clus_wtc)

#4)Infomap
clus_inf<- cluster_infomap(g1)
communities(clus_inf)
modularity(clus_inf)

#5)Leading eligen
clus_evc<- cluster_leading_eigen(g1)
communities(clus_evc)
modularity(clus_evc)

#6)Label propagation
clus_lpc<- cluster_label_prop(g1)
communities(clus_lpc)
modularity(clus_lpc)
```

#[4]--------------RETURN ALGORITHM NAME FOR THE HIGHEST MODULARITY SCORE-------------------------------

```{r}
algorithms<- cbind(c(clus_btw$algorithm, clus_sgc$algorithm, clus_wtc$algorithm, clus_inf$algorithm, clus_evc$algorithm, clus_lpc$algorithm))
algorithms<- as.data.frame(algorithms)

mod_score<- cbind(c(modularity(clus_btw), modularity(clus_sgc), modularity(clus_wtc), modularity(clus_inf), modularity(clus_evc), modularity(clus_lpc)))
mod_score<- as.data.frame(mod_score)

final<- cbind(algorithms, mod_score)
colnames(final) <- c("Algoritms", "Modularity score")

str(final)
#convert from factor to character
final$Algoritms<- as.character(as.factor(final$Algoritms))

score<- max(final$`Modularity score`)
final[final$`Modularity score` == score, "Algoritms"]

```


#[5]----------RETURN TOP 2 ALGORITHMS GIVING HIGHEST MODULARITY SCORE-----------------------------------

```{r}
##arrange dataframe in ascending order of modularity score
top2_score<- final[ order(-final[,2], final[,1]), ]
top2_score[1:2,]

```


######system.time({
    
#clus_sgc<- cluster_spinglass(g1)
#  })

#[6]----------PLOT THE MODULARITY SCORE AGAINST ALGORITHMS-----------------------------------

```{r}
#Plot the values

library(plotly)

p <- plot_ly(
    x = final$Algoritms,
    y = final$`Modularity score`,
    name = "SF Zoo",
    type = "bar"
)
p
```
###Comparing communities from differnt algorithm i.e to find distance between 2 community structure

#TODO
#also rank the community detection algorithm based on execution time and modularity

#convert communities to dataframe
#com <- cbind(V(g1)$name,clus_sgc$membership)